Contention management for Cloud RAN over an optical ring

### 2018-06-06 ISCIS/article.tex
conflits

\begin{prop}
\label{prop:assign}
There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
\end{prop}
\begin{proof}
 We fix $m_1 = 0$ and all the offsets will also be at position $0$. 
 Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$. We assume that $u_1,\dots,u_k$ are in the order of the ring. The last message emitted by the RRH $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$. Therefore we can fix $m_2 =  ET  + \omega(u_1,u_2)$. In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$. The assignment is correct, if when the RRH $1$ must emit something in the second period, there is a free container. It implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.\qed
\end{proof}

\begin{corollary}
The number of antennas supported by a ring is $K = \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$
\end{corollary}
\begin{proof}
Following Prop.~\ref{prop:assign}, the number of antennas on a position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
Since we need two positions for $k$ antennas, in order to carry the traffic coming from the RRHs and the BBUs, and we got $F$ positions in the slot, the number of antennas supported by the ring is thus equal to $k \times \frac{F}{2}$.\qed
\end{proof}
Remark that for each position which is used by some RRH, $RS$ containers are reserved before starting to emit some C-RAN traffic. Those containers which are reserved could either be free or freed during the next round trip. Thus, those containers are seen by the BE traffic as additional dataflow.
Therefore to not waste much bandwidth, it is relevant to put as many RRH as possible on the same position. Moreover, unused positions in an assignment are useful to guarantee a good latency to BE traffic. The unused positions can be distributed uniformly over a slot, to minimize the time to wait before a free container, as shown in Fig.~\ref{fig:repart1}.

>>>>

\begin{prop}
\label{prop:assign}
There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if and only if $k\times ET + RS \leq P$, t
\end{prop}
\begin{proof}
 We fix $m_1 = 0$ and all the offsets will also be at position $0$. 
 Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$. We assume that $u_1,\dots,u_k$ are in the order of the ring. The last message emitted by the RRH $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$. Therefore we can fix $m_2 =  ET  + \omega(u_1,u_2)$. In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$ during a period. The assignment is correct, since when the RRH $1$ must emit something in the second period, there is a free container. This later constraint implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.\qed
\end{proof}

\begin{corollary}
The maximal number of antennas supported by a ring is $K = \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$
\end{corollary}
\begin{proof}
Following Prop.~\ref{prop:assign}, the number of antennas on a position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
Since we need two positions for $k$ antennas, in order to carry the traffic coming from the RRHs and the BBUs, and we got $F$ positions in the slot, the number of antennas supported by the ring is thus equal to $k \times \frac{F}{2}$.\qed
\end{proof}
Remark that for each position which is used by some RRH, $RS$ containers are reserved before starting to emit some C-RAN traffic. Those containers which are reserved could either be free or freed during the next round trip. Thus, those containers are seen by the BE traffic as additional dataflow.
Therefore to not waste much bandwidth, it is relevant to put as many RRH as possible on the same position. Moreover, unused positions in an assignment are useful to guarantee a good latency to BE traffic. The unused positions can be distributed uniformly over a slot, to minimize the time to wait before a free container, as shown in Fig.~\ref{fig:repart1}.
